Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-23 paper/icml_drau/experiments.tex
Removed Normalized epoch

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiments provided here are specifically aimed at showing that
the proposed method, DAU, works efficiently over a wide range of time
discretizations, without specific tuning, while standard deep $Q$-learning
approaches do not. DAU is compared to DDPG for continuous actions and to
DQN for
discrete actions.
Since we focus on $Q$-learning-like off-policy methods, we do not
compare against on-policy methods (A3C~\cite{a3c}, PPO~\cite{ppo},
TRPO~\cite{trpo}...).

@@

We plot the learnt policy at several instants in physical time
(normalized epochs) during training, for various time discretizations
$\deltat$, for both DAU and DDPG. With DAU, the agent's policy and value
function quickly converge for every time discretization without specific
tuning. On the contrary, with DDPG, learning of both value function and
policy vary greatly from one discretization to another.

>>>>

%! TEX root = icml_drau.tex
\section{Experiments}
\label{sec:exp}
\input{lc_fig.tex}
The experiments provided here are specifically aimed at showing that
the proposed method, DAU, works efficiently over a wide range of time
discretizations, without specific tuning, while standard deep $Q$-learning
approaches do not. DAU is compared to DDPG for continuous actions and to DQN
for discrete actions.  As mentionned earlier, we do not study the time
discretization invariance of on-policy methods (A3C, PPO, TRPO...).

@@

We plot the learnt policy at several instants in physical time
during training, for various time discretizations
$\deltat$, for both DAU and DDPG. With DAU, the agent's policy and value
function quickly converge for every time discretization without specific
tuning. On the contrary, with DDPG, learning of both value function and
policy vary greatly from one discretization to another.
